The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-05 paper/ms.tex
aerts affiliation

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6}$
Timothy R. White,$^{7,5}$\newauthor
Amalie Stokholm,$^{5}$
Allyson Bieryla,$^{8}$
David W. Latham,$^{8}$
Conny Aerts,$^{9,10,11}$\newauthor
Suzanne Aigrain,$^{3}$ 
Victoria Antoci,$^{5}$
Timothy R. Bedding,$^{12,5}$
Dominic M. Bowman,$^{9}$\newauthor
Ashley Chontos,$^{13}$
Gilbert A. Esquerdo,$^{8}$
Daniel Huber,$^{13}$
Paula Jofr\'{e},$^{14}$\newauthor
Madeline Lucey,$^{6}$
Simon J. Murphy,$^{12,5}$
Timothy van Reeth,$^{12,5}$\newauthor
Victor Silva Aguirre,$^{5}$
Jie Yu$^{12,5}$ 
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{8}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{9}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{10}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{11}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
$^{12}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{14}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

@@

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology both for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C} and for coherent heat-engine driven oscillations \citep{2018arXiv180907779A}. It has yielded the detection of gravity-dominated mixed mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2016MNRAS.456.2183D,2018MNRAS.479.4786V}. \kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{2015ApJ...810...16T,2018A&A...618A..24V}. %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence.

@@

The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue that is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}. We have adopted the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of either the first~4 or~8 CBVs to each light curve. This can remove astrophysical signals having long timescales, and so we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, or indeed raw uncorrected lightcurves for stars variable at high amplitude on $\sim$~quarter timescales, but otherwise we recommend the 8~CBV light curves. There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper. In the following, we use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} CDPP implementation \citep{k2sc}. This is not necessarily the optimal choice for all red giants, especially those with oscillations on a 6.5~h timescale, but is a reasonable proxy for white noise and leads to satisfactory results upon visual inspection of the present sample.

>>>>

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6}$
Timothy R. White,$^{7,5}$\newauthor
Amalie Stokholm,$^{5}$
Allyson Bieryla,$^{8}$
David W. Latham,$^{8}$
Conny Aerts,$^{9,10}$\newauthor
Suzanne Aigrain,$^{3}$ 
Victoria Antoci,$^{5}$
Timothy R. Bedding,$^{11,5}$
Dominic M. Bowman,$^{9}$\newauthor
Ashley Chontos,$^{12}$
Gilbert A. Esquerdo,$^{8}$
Daniel Huber,$^{12}$
Paula Jofr\'{e},$^{13}$\newauthor
Madeline Lucey,$^{6}$
Simon J. Murphy,$^{11,5}$
Timothy van Reeth,$^{11,5}$\newauthor
Victor Silva Aguirre,$^{5}$
Jie Yu$^{11,5}$ 
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{8}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{9}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{10}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{11}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{12}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{13}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

@@

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology both for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C} and for coherent heat-engine driven oscillations \citep{2018arXiv180907779A}. It has yielded the detection of gravity-dominated mixed mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2016MNRAS.456.2183D,2018MNRAS.479.4786V}. \kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{2015ApJ...810...16T,2018A&A...618A..24V}. %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence. 
\newpage

@@

The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue that is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}. We have adopted the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of either the first~4 or~8 CBVs to each light curve. This can remove astrophysical signals having long timescales, and so we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, or indeed raw uncorrected light curves for stars variable at high amplitude on $\sim$~quarter timescales, but otherwise we recommend the 8~CBV light curves. There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper. In the following, we use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} CDPP implementation \citep{k2sc}. This is not necessarily the optimal choice for all red giants, especially those with oscillations on a 6.5~h timescale, but is a reasonable proxy for white noise and leads to satisfactory results upon visual inspection of the present sample.
